Contribution Title\thanks{Supported by organization x.}

### 2020-02-02 sections/i_uip.tex
sync up once again
add an example to illstruate i-uip, i-uip-pure and i-uip-min

>>>>

\begin{example}
Consider the assertion trail $\assertionTrail = {..a_2,b_2,c_2,d_2..e_5,f_5,g_5,h_6,i_6,j_6,k_6..}$ where literals $a_2 ... k_{6}$ are asserted in order with decision level shown as the underscript. Let $L_{ext}$ denote the set of literals on $\assertionTrail$ outside of decision level 2,5,6 and 10, and $l^{*}_{ext}$ be some literal in $L_{ext}$. The reasoning clauses involved in building $\assertionTrail$ are:
\begin{enumerate}
  \item[] $C_k = \{\neg{f_5} \vee \neg{j_6} \vee k_6\}$,
  $C_j = \{\neg{f_5} \vee \neg{i_6} \vee j_6\}$, 
  $C_i = \{\neg{e_5} \vee \neg{h_6} \vee i_6\}$,
  $C_g = \{\neg{a_2} \vee \neg{f_5} \vee g_5\}$
  $C_f = \{\neg{l^{*}_{ext}} \vee \neg{e_5} \vee f_5\}$,
  $C_d = \{\neg{b_2} \vee \neg{c_2} \vee d_2\}$,
  $C_c = \{\neg{a_2} \vee \neg{b_2} \vee c_2 \}$,
  $C_b = \{\neg{l^{*}_{ext}} \vee \neg{a_2} \vee b_2\}$
\end{enumerate}
Suppose 1-UIP learning produces clause 
$\oneUIPClause = \{\neg{m_{10}} \vee \neg{k_6} \vee \neg{j_6} \vee \neg{i_6} \vee \neg{h_6} \vee \neg{g_5} \vee \neg{d_2} \vee \neg{c_2}\}$ where $\neg{k_{10}}$ is the UIP from the conflicting level. $\IUIP$ first tries to find the UIP for level 6 by resolving $\oneUIPClause$ with $C_k$, $C_j$ and, $C_i$ in order and produces clause 
$\iUIPClause = \{\neg{m_{10}} \vee \neg{h_6} \vee \neg{g_5} \vee \neg{f_5} \vee \neg{e_5} \vee \neg{d_2} \vee  \neg{c_2} \}$ where $\neg{h_6}$ is the UIP.

$\IUIP$ attempts to find the UIP for level 5 by resolving $C_i$ with 
$C_g$ and $C_f$ in order. However, resolving with $C_f$ will introduce $\neg{l^{*}_{ext}}$ into 
$C_i$ and increase the clause's LBD. $\IUIPPURE$ undoes all resolutions at level 5 and skips the entire level, whereas $\IUIPMIN$ only skips the resolution with $C_f$ and tries to find the UIP by ignoring $\neg{f_5}$.  After level 5, $\IUIPPURE$ preserves the same clause and $\IUIPMIN$ produces $\iUIPClause = \{\neg{m_{10}} \vee \neg{h_6} \vee \neg{f_5} \vee \neg{e_5} \vee \neg{d_2} \vee \neg{c_2} \vee \neg{a_2}\}$ where $\neg{e_5}$ is the UIP when $\neg{f_5}$ is ignored. The same $\IUIP$ procedure is then performed on level 2 to produce the final $\iUIPClause$.

$\IUIPPURE$ learned $\iUIPClause = \{\neg{m_{10}} \vee \neg{h_6} \vee \neg{g_5} \vee \neg{f_5} \vee \neg{e_5} \vee \neg{d_2} \vee  \neg{c_2} \}$ and reduces the learnt clause size by 1. $\IUIPMIN$ learned $\iUIPClause = \{\neg{m_{10}} \vee \neg{h_6} \vee \neg{f_5} \vee \neg{e_5} \vee \neg{b_2} \vee \neg{a_2}\}$ and reduces the learnt clause size by 2. 
\end{example}
